Silica-based integrated 1$\times$4 polarization beam splitter module for free-space BB84 quantum key distribution

### 2017-09-04 manuscript.tex
comment deleted

\begin{document}
\title{Silica-based integrated 1$\times$4 polarization beam splitter module for free-space BB84 quantum key distribution}
\author{Joong-Seon Choe, Heasin Ko, Byung-Seok Choi, Kap-Joong Kim, and Chun Ju Youn}
\address{Electronics and Telecommunications Research Institute, Daejeon 34129, Korea}
\email{jschoe@etri.re.kr}
%\thanks{Joong-Seon Choe is with ETRI.}
%\maketitle
\begin{abstract}
% 편광기반 BB84 프로토콜 기반의 QKD에 사용하기 위해 실리카 PLC 기술로 집적형 편광 분할/결합기 모듈을 개발했다.
We have developed an integrated polarization beam splitter (PBS) module with silica planar lightwave circuit technology for use in BB84 quantum key distribution (QKD).
% 4개의 편광에 대해 동작시키기 위해 반파장판을 삽입하였으며, 모듈의 편광소광비와 삽입손실은 각각 ___ dB와 ___ dB였다.
The PBS module was designed to operate on four linear polarizations of horizontal/vertical/diagonal/antidiagonal direction, and showed the minimum polarization extinction ratio of 17.6 dB.
%The excess optical loss and The minimum polarization extinction ratio were \underline{4.59} dB and \underline{17.6 dB}, respectively.
% 무선양자암호 테스트베드에 장착하였을 때 QBER과 sifted key rate은 까각 ___%와 ___kbps롤 보였다.
When the module was loaded on the free-space BB84 QKD test-bed, quantum bit error rate and sifted key rate  were 2.81\% and 415 kbps at clock rate of 100 MHz, respectively.
\end{abstract}

@@

\section{Introduction}
%최근에 통신 보안에 대한 이슈가 부각되면서 양자암호통신에 대해 많은 연구가 이루어지고 있다.
Many researches have been conducted for quantum communication as security solution is one of the main issues in communication technology \cite{Bennett:1984is, Ekert:1991kl,Ko:2017cs}.
%양자 암호 통신을 위한 여러 프로토콜들 중 최초로 제안된 BB84는 가장 많이 연구되어 오고 있다.
Since Bennett and Brassard proposed BB84 protocol for secure key distribution, it has widely been chosen for quantum key distribution (QKD) \cite{Bennett:1984is}.
% BB84를 구현하기 위해서 직교하지 않는 두 베이시스 셋을 구성하며 그 수단으로 주로 편광 또는 위상을 사용한다.
Implementation of BB84 requires two sets of non-orthogonal basis %that can be constructed with either polarization or phase.
% 광신호의 전달 매체는 환경에 따라서 자유공간 또는 광섬유가 사용된다.
% 자유공간 BB84 통신에서는 편광이 잘 유지가 되므로 편광으로 신호 인코딩이 가능하다.
that are usually constructed with polarization of single photon for free-space communication.
% 광섬유를 사용할 경우 광섬유가 받는 스트레인에 의해 발생하는 복굴절이 편광의 변화를 유발하므로 원래의 편광을 유지하는 것이 어려우므로 흔히 빛의 위상으로 신호를 인코딩한다.
% 자유 공간에서는 상대적으로 편광의 변화가 적으므로 편광 인코딩의 BB84 프로토콜의 사용이 용이하다.
% 편광 기반의 BB84는 HV 또는 DA 편광으로 이루어진 베이시스 중 하나를 선택하고 선택한 베이시스의 두 편광 중 하나를 선택함으로써 데이터를 인코딩하여 보내는 방식으로 암호키를 전달한다.
The polarization-based BB84 protocol encodes the data by choosing a basis of the two bases of horizontal(H)/vertical(V) or diagonal(D)/antidiagonal(A) polarization, and transmitting a single photon of a polarization from the chosen basis to generate an encryption key.
%HVDA의 네 편광 중 하나를 선택해서 보내고 수신자는 편광을 가반으로 한 많은 연구가 수행되어 왔다.
%Polarization-based BB84 generally uses single photons with horizontal (H), vertical (V), diagonal (D), and antidiagonal (A) polarization

Thus an optical part for splitting or combining the four states of polarization is essential for a polarization-based BB84 QKD, and is generally composed of two bulk polarization beam splitters (PBS), one beam splitter, and one half-wave plate (HWP) \cite{Ko:2017cs}.
%편광을 합치고 보내는 광학계는 일반적으로 벌크 광학 부품을 정렬하여 사용하는데, 양자비트에러율은 광정렬의 정확도에 크게 의존하므로 시간이 지남에 따라 발생할 수 있는 약간의 정렬 틀어짐도 시스템의 안정성을 떨어뜨리게 된다.
Although the bulk-optic components show high performances in polarization extinction ratio (PER), optical loss, and so on, the QKD system will work only when the components are installed with high alignment accuracy upon which its overall performance is strongly dependent.
%In addition, some alignment drift over time can degrade system stability even though initial alignment status results in sufficiently low QBER.
%본 연구에서는 자유공간을 통한 편광 기반의 BB84 프로토콜 양자암호통신의 구현을 위해 광도파로 소자로 구현된 편광분할기 모듈을 개발하였고 무선 양자암호통신 테스트베드에 장착하여 키 분배 실험을 수행하였다.

The need for alignment of discrete optic components can be removed if they are replaced by  a passive photonic chip with integrated elements
%If the optical components are replaced by integrated elements on a chip
fabricated through semiconductor processes such as photo-lithography and dry etching.
The chip-scale integration of the optical part of BB84 system provides miniaturization necessary to diversify application area such as QKD for hand-held devices, and makes it possible to achieve mass production with low cost.
In view of performance, the integration improves stability of QKD system because optical transmission characteristics of a passive photonic chip is quite stable.
%Integration of all the components on a chip removes the alignment processes and prevents the drift of alignment over time that can degrade system stability even though initial alignment status results in sufficiently low QBER.
%The chip-scale integration provides performance stability improvement as well as miniaturization of optical part in BB84 system, and can readily be implemented using waveguide-based photonic circuit technology.
PBS chips using waveguide are widely used in optical receivers for polarization-multiplexed modulation formats such as dual polarization quadrature phase shift keying (DP-QPSK), dual polarization 16 quadrature amplitude modulation (DP-16QAM), etc  \cite{Lee:2016bg,PoDong:2014kj}.
However, there has been no report on integrated PBS chip that can deal with four polarizations used in BB84 QKD.
In this study, integrated PBS module using  silica-based planar lightwave circuit (PLC) chip was fabricated for the first time for BB84 protocol, and its performance was assessed it in a free-space QKD test-bed.

@@

% PBS 소자는 실리콘 기판 위에 실리카 평판형 광도파로를 이용하여 제작하였다.
PBS developed in this work is based on Mach-Zehnder interferometer (MZI) structure fabricated with silica PLC technology, as is shown in Fig. \ref{fig:layout}(a)\cite{Kim:2012ej, Hashizume:2015ta}.
% 사용하는 파장 대역이 780 nm이므로 여기에서 단일 모드가 되며 해당 파장에서의 광섬유와 높은 광결합 효율을 가지도록 기본 도파로를 설계하였다.
The waveguide structure was chosen to support single mode and maximum mode matching with single mode fiber (SMF) at the operating wavelength of 780 nm, where Si-based single photon detector has high detection efficiency and atmospheric absorption is low.
% 코어와 클래드의 굴절률은 780 nm의 파장에서 각각 ___와 ___였으며 도파로 코어의 크기는 가로와 세로가 모두 4.3 um이다.
Refractive indices of core and clad material were 1.4588 and 1.4537 at 780 nm, respectively, and the dimension of the waveguide core was designed as 4.3 $\mu$m $\times$ 4.3 $\mu$m.
% 마흐 젠더 간섭계 구조에서 한 쪽 arm에서 수직과 수평의 두 편광간에 180도의 retardation이 나타나도록 하고 다른 쪽 arm과는 두 편광이 모두 90도의 위상차가 존재하도록 하면 두 편광을 분리할 수 있다.
%In the MZI structure, H- and V-polarizations can be separated by providing a retardance of 180$^\circ$  between the two polarizations in one arm while both the polarizations have phase difference of 90$^\circ$  between the two arms \cite{Kim:2012ej}.
% retardation을 가하기 위해 한 쪽 arm의 도파로 일부를 넓게 설계하였다. 이렇게 하면 제작 공정상에서 uniaxial strain을 받게 되어 복굴절이 발생함이 알려져 있으며, 복굴절 * 길이 * 2pi / 파장 = 2m*pi+pi 가 되는 길이로 제작하면 180도의 위상차가 되게 만들 수 있다.

In Fig. \ref{fig:layout}(a), the input light is split into two paths by a 3 dB splitter.
At the outputs of the splitter are connected in parallel two identical MZIs with 2$\times$2 multimode interference (MMI) coupler.
%Each birefringent MZI in this device splits the input light into H- and V-polarized light.
A portion of the waveguide of upper arm in each MZI was designed to have larger width of 18.5 $\mu$m.
A wide waveguide in silica PLC is known to have birefringence  due to uniaxial strain generated in the fabrication process \cite{Okuno:1994fm}.
%The birefringence causes H- and V-polarized lights hav
The birefringence causes relative phase differences between H- and V-polarized lights when light reaches the  input of the MMI through the arms.
When the device is designed so that birefringence $\Delta n$ and length $L$ of the wide waveguide satisfy the condition $2\pi\Delta n/\lambda  = (2m+1) \pi$ with integer $m$, the phase difference between H- and V-polarization can be made to be 180$^\circ$.
% The required retardance was provided by designing part of one arm in MZI widely.
% Wide waveguide in silica PLC was known to suffer uniaxial strain and therefore birefringence occurs.
% As retardance is
%다른 한 쪽 arm의 길이도 적절히 설계하면 위의 모든 위상 조건을 만족하도록 하는 것이 가능하다.
If above condition is satisfied and the lower arm is made to provide a phase difference of 90$^\circ$ between the arms for the two polarizations, polarization separation is achieved according to the operation of MMI depicted in Fig. \ref{fig:layout}(b).
%If the lower arm of the MZI provides phase difference of 90$^\circ$ between the two arms for both the polarizations, is designed so that phase difference of 90$^\circ$ occurs between the two input ports of the MMI for both the polarizations, the polarization of each polarization will only come out to different output ports of the MMI due to the nature of the MMI.
%If the length of the other arm is properly designed, it is possible to satisfy the aforementioned phase relationship.
% % TE and TM polarization can be split if they have phase difference of $\pi$ in one arm of MZI and $\pi/2$ between the two arms, as described in    .
% Part of an arm of MZI was designed to have wide width to impose retardance.
% Wide waveguide is known to result in uniaxial strain and thus birefringence occurs.
% As retardance is
% \begin{equation}
%   \Delta n_{br}L \times 2\pi / \lambda
% \end{equation},
%appropriate length can give phase difference of $\pi$..
%\subsection{P\Delta n_{br}L \times BS chip}2\pi / \lambda
%The other arm of MZI can meet above phase relation for polarization splitting with appropriate length.
%그러나, 위상 조건은 길이에 의해서 정해지나 실제로 온도의 변화에 따라서 민감하게 달라지므로 간섭계 구조를 사용할 경우 active 하게 조절하는 것이 필요하다.

The phase relationship is determined by arm length, as described above.
But actually it changes sensitively with ambient temperature around the interferometer structure.
%따라서 본 연구에서는 간섭계의 arm에 히터를 장착하여 전류로 위상을 조절할 수 있도록 했다.
Therefore, micro-heaters were deposited on the arms of MZI to actively control the phase making use of the thermo-optic property of silica.

The input light may be in D/A-polarization basis as well as H/V-polarization basis, but D- and A-polarized light can not be properly separated in PLC PBS composed of rectangular waveguide.
% 따라서 본 연구에서는 두 MZI중 하나의 입력부에 slit을 형성하고 광축이 22.5도 기울어진 반파장 필름을 삽입하여 DA에서 HV로 편광을 바꾼 후 분리하는 방법을 취했다.
In this study, a HWP film with its optic axis tilted by 22.5$^\circ$ was inserted at the input of the lower PBS to split D/A polarization.
Although the output of the lower MZI is annotated as D/A in Fig. \ref{fig:layout}, actual polarization of the output light is H/V.

%다음 그림은 소자의 설계 도면과 제작이 완료된 칩바의 사진이다.

%Figure \ref{fig:layout} shows the layout of the device.
% and photograph taken after fabrication process is completed.
%The input light is split into two paths by the 3 dB splitter.
%At the outputs of a 3 dB splitter are connected in parallel the two identical birefringent MZIs with 2$\times$2 multimode interference device at their outputs.
%Each birefringent MZI in this device splits the input light into H- and V-polarized light.
%The input light is split into two paths by the 3 dB splitter and separated into H-and V-polarized light in each PBS.
%The PBS splits H and V while input polarization can be D or A, thus a half-wave plate is to be inserted in front of the lower PBS.
%소자의 길이는 42 mm 이고 폭은 1.2 mm 이다.
%Each device is 42 mm and 2.3 mm in length and width.
%Figure \ref{fig:device} shows layout of the device developed in this study.
\begin{figure}
  \centering
  \includegraphics[height=6.3cm]{./layout}
  \caption{(a) Layout of the PBS device for H/V/D/A-polarizations. 1$\times$2 splitter splits the input light into two PBSes that separate H- and V-polarization and output them to the corresponding waveguides. Lower PBS has HWP at its input so that D- or A-polarized light is converted to H- or V-polarization. (b) Schematic description of the operation of 2$\times$2 MMI. Under single port input, the two outputs show electric field with same amplitude and relative phase difference of 90$^\circ$ (upper). If there is phase difference of 90$^\circ$ between two input electric fields, one output is extinguished (lower).}
  \label{fig:layout}
\end{figure}
% 입력된 빛은 1X2 splitter에서 갈라지고 각각 HV에 대한 PBS에서 편광별로 분리되어 각각의 출력으로 나가도록 되어 있다.
% 입력되는 빛은 HV 뿐만 아니라 DA 베이시스인 경우도 있으나 사각도파로로 구성된 PLC PBS에서 D와 A를 제대로 분리할 수 없다.

%Therefore, in this study, a HWP film was inserted in a slit formed a slit is formed on one input of two MZIs, and a HWP film with optic axis tilted by 22.5$^\circ$ is inserted to change polarizations from DA to HV and then separated.
% 이것은 벌크 옵틱스로 꾸민 BB84 광학계에서 사용하는 방법과 동일하다.
%This is the same method used in the general BB84 system with bulk optics.
%칩바 상태에서 편광 분리 특성을 측정하기 위해 다음 그림과 같은 측정 셋업을 사용하였다.

% Measurement  of Fig. \ref{fig:setup}  was used to characterize the polarization splitting property of the device without pigtailed fiber.
% \begin{figure}
%   \centering
%   \includegraphics[width=10cm]{./setup}
%   \caption{}
%   \label{fig:setup}
% \end{figure}
% Output of a 780 nm DFB LD was delivered to a PBS chip through a polarization-maintaining fiber (PMF) whose slow axis is aligned obliquely so that incident light contains both H- and V-polarization.
% The output lights was expaned through an objective lens and observed using a beam profiler\underline{(Ophir Optronics Spiricon SP503)}.
% As the input is neither H nor V, output light has both the polarizations.
% In order to evaluate PER, a linear polarizer (LP) was placed between the objective lens and beam profiler.
% If the transmission axis of the LP is vertical, only V-polarized light is considered to be incident since the LP filters out the H-polarized light with extinction ratio exceeding 30 dB.
% This method is based on the assumption that rotation of polarization does not occur for H- and V-polarized lights.
% With polarization rotation, PER would be deteriorated when measured after the chip is fabricated to PBS module that does not contain any LP.
% As will be discussed later, however, PBS module does not show any drop of PER, which suggests the validity of the assumption.

\subsection{Half-Wave Plate Film}
%위의 파장분할기는 수직과 수평 편광의 분할 기능을 가지며, 45도와 135도의 편광에 대해서는 진행중의 회전 때문에 동작을 보장할 수 없다.
%PBS described above has function of separating H and V polarization, and does not work for D and A polarization.
%따라서 두 대각 편광을 수직 또는 수평 편광으로 바꿔주기 위한 반파장판을 도파로 중간에 삽입한 후 편광 분리 동작을 하도록 하기 위해 780 nm 파장대역용 박막 반파장판을 제작하였다.
Thin film HWP was developed for converting D/A polarization to H/V polarization that can be inserted in a slit across a waveguide.
A HWP was fabricated by imposing birefringence on a polymer film \cite{Ando:1993up}.
% 사용한 필름은 폴리카보네이트이고, 175도에서 45% 길이만큼 잡아늘여서 복굴절을 일으켰다.
Fixed at its two sides on a metal frame designed for elongation process, the film was stretched at an elevated temperature.
% 여러 조건에 대해서 필름의 연신 공정을 수행한 결과 50um 두께의 PC 필름을 40% 길이만큼 연신했을 때 반파장에 근접한 retardance를 보임을 확인했다.
Elongation process was performed for several kinds of commercial polymer film under various conditions, and it was found that 40\% elongation of 60-$\mu$m-thick polycarbonate film at 170$^\circ$C resulted in retardance near 180$^\circ$ at the wavelength of 780 $\mu$m.
The thickness of the film after process was 53 $\mu$m.
%45도/135도 편광의 입사광에 대해 사용하여야 하므로 광축을 수평면에 대해 22.5도 기울어지게 잘라내었다.
As the film was to be used for light of D/A polarization, cutting direction was selected so that the optic axis was inclined by 22.5$^\circ$ with respect to the bottom side of the film.

\subsection{PBS Module}
%우선 dicing blade로 병렬로 이어져있는 두 간섭계의 입력부 부분에 홈을 내고 반파장판 필름을 삽입하고 에폭시로 고정하였다.

Firstly, a narrow groove was formed at the input waveguides of two parallel MZIs comprising 1$\times$4 PBS with a dicing blade for the insertion of the waveplate film.
% 반파장판은 한 쪽 간섭계에만 필요하나 두 간섭계간의 거리가 가까와서 dicing blade로는 양 쪽 모두에 홈을 낼 수밖에 없다.
Waveplate is needed for only one MZI of the PBS, but the groove spans  both the MZIs because of the small separation of 500 $\mu$m, resulting in similar optical loss between the two MZIs.
% 그러나 이러한 한계가 실제로는 두 간섭계의 손실 차이를 줄이는 장점도 제공한다.
%This limit in process, however, provides merit of small imbalance in loss between the two MZIs.
% 50 um 두께의 블레이드로 공정하였을 때 실제로 형성된 홈의 폭은 약 60 um 정도였고, 이 간격과 chipping에 의해 발생하는 광손실은 ___ dB였다.
When processed with 50-$\mu$m-thick blade, the width of the groove formed was about 62 $\mu$m.
After the waveplate film was inserted into the groove, UV-cured epoxy was injected to fix it.
%The epoxy reduces the effect of chipping and divergence angle of the light emitted from the waveguide.
%Tha gap and chipping caused optical loss of \underline{088-49502} dB.
% 에폭시를 주입하였을 때 chipping의 효과를 줄이고 빛의 diverging도 줄이므로 손실은 ___ dB 정도로 감소하였다.
%The optical insertion loss was $\underline{04820825}$ dB including optical coupling loss, scattering loss at the slit, and radiation loss occurring on the optical path in the PBS device.
% 이론적으로 홈의 폭을 30 um 로 줄이면 손실은 ___ dB 정도로 줄어들므로 얇은 반파장판의 제작이 전체적인 특성 개선을 가져올 것으로 기대된다.
%Simulation predicts that the reduced width of the slit to 30 $\mu$m will reduce the optical loss by \underline{1.5} dB.
%Thus using thinner waveplate film and blade will help improve optical loss by about 1.5 dB.
% 1X4 구조의 칩에서 한 쪽은 단일모드 광섬유를, 다른 한 쪽은 4채널의 편광유지 광섬유를 8도 angle polishing을 하여 피그테일하였다.

Pigtailed were an SMF on the input facet and 4-channel polarization-maintaining fiber (PMF) array on the output facet.
Both the PBS chip and fibers were angle (8$^\circ$)-polished to reduce the optical return loss that influences the stable operation of LD.
The four PMFs were aligned so that the slow-axes  were oriented alternately as H-V-H-V.
Using this PMF array, the module can be used as polarization beam combiner (PBC) as well as PBS.
% 사전에 TEC와 thermistor 가 장착된 하우징에 피그테일된 칩을 고정하고 전극을 와이어 본딩하여 모듈 조립을 완료하였다.

@@

\section{Characterization}
\subsection{PBS chip}
% 편광 소광비 측정을 위해 다음 그림과 같은 측정 셋업을 구성하였다.
% \begin{figure}
%   %\includegraphics{}
%   \caption{PER measurement setup}
%   \label{fig:PER_setup}
% \end{figure}

@@

% PMF의 광축을 약 45도 정도 기울어지도록 설치한 후 칩에 정렬하여 빛을 입사시켰다.
%Laser output was launched on the chip through PMF whose optic axis was inclined by 45$^\circ$.
% 칩을 통과한 빛에는 H와 V 편광이 섞여있으며, 대물렌즈를 거쳐서 나오는 빛을 선형 편광판을 이용하여 측정하고자 하는 편광만을 걸러낸 후 빔프로파일러를 이용하여 출력 도파로로부터의 빛의 세기를 측정하였다.
% The light passing through the chip, whose polarization was mixed with H and V direction, was focused by an objective lens and filtered using a linear polarizer to either H or V polarized light.
PER was obtained by measuring the intensity from the output waveguides using a beam profiler while the current of the micro-heater was adjusted so that PER of PBS could be maximized.

% PBS 칩은 복굴절 도파로의 길이에 따라 다른 편광소광비 특성을 보였다.
The PBS chip showed different PER characteristics depending on the length of the birefringent waveguide (BRW) as shown in Fig. \ref{fig:BRW-PER}.
\begin{figure}
  \centering
  \includegraphics[width=7cm]{./BRWPER.pdf}
  \caption{Measured result of PER with birefringent waveguide length. Maximum PER of 17.1 dB was obtained when the BRW length is 2624 $\mu$m.}
  \label{fig:BRW-PER}
\end{figure}
% 최대의 편광소광비가 얻어지는 조건의 복굴절 도파로 길이는 약 ___ um 정도로, 이 길이에서 H와 V 간에 180도 위상차가 발생한다.
Maximum PER was measured as 17.1 dB  when the length of BRW was 2624 $\mu$m.
 %where H- and V- polarization show phase difference of 180$^\circ$.
From this result, the birefringence of the BRW is estimated as 1.5$\times 10^{-4}$ that is similar to that reported in Ref. \cite{Hashizume:2015ta}.

% 본 연구에서 제작한 칩에서는 히터를 동작시켜야만 편광이 분리되었다.

>>>>

\begin{document}
\title{Silica-based integrated 1$\times$4 polarization beam splitter module for free-space BB84 quantum key distribution}
\author{Joong-Seon Choe, Heasin Ko, Byung-Seok Choi, Kap-Joong Kim, and Chun Ju Youn}
\address{Electronics and Telecommunications Research Institute, Daejeon 34129, Korea}
\email{jschoe@etri.re.kr}

\begin{abstract}
We have developed an integrated polarization beam splitter (PBS) module with silica planar lightwave circuit technology for use in BB84 quantum key distribution (QKD).
The PBS module was designed to operate on four linear polarizations of horizontal/vertical/diagonal/antidiagonal direction, and showed the minimum polarization extinction ratio of 17.6 dB.
When the module was loaded on the free-space BB84 QKD test-bed, quantum bit error rate and sifted key rate  were 2.81\% and 415 kbps at clock rate of 100 MHz, respectively.
\end{abstract}

@@

\section{Introduction}

Many researches have been conducted for quantum communication as security solution is one of the main issues in communication technology \cite{Bennett:1984is, Ekert:1991kl,Ko:2017cs}.
Since Bennett and Brassard proposed BB84 protocol for secure key distribution, it has widely been chosen for quantum key distribution (QKD) \cite{Bennett:1984is}.
Implementation of BB84 requires two sets of non-orthogonal basis
that are usually constructed with polarization of single photon for free-space communication.
The polarization-based BB84 protocol encodes the data by choosing a basis of the two bases of horizontal(H)/vertical(V) or diagonal(D)/antidiagonal(A) polarization, and transmitting a single photon of a polarization from the chosen basis to generate an encryption key.

Thus an optical part for splitting or combining the four states of polarization is essential for a polarization-based BB84 QKD, and is generally composed of two bulk polarization beam splitters (PBS), one beam splitter, and one half-wave plate (HWP) \cite{Ko:2017cs}.
Although the bulk-optic components show high performances in polarization extinction ratio (PER), optical loss, and so on, the QKD system will work only when the components are installed with high alignment accuracy upon which its overall performance is strongly dependent.

The need for alignment of discrete optic components can be removed if they are replaced by  a passive photonic chip with integrated elements
fabricated through semiconductor processes such as photo-lithography and dry etching.
The chip-scale integration of the optical part of BB84 system provides miniaturization necessary to diversify application area such as QKD for hand-held devices, and makes it possible to achieve mass production with low cost.
In view of performance, the integration improves stability of QKD system because optical transmission characteristics of a passive photonic chip is quite stable.
PBS chips using waveguide are widely used in optical receivers for polarization-multiplexed modulation formats such as dual polarization quadrature phase shift keying (DP-QPSK), dual polarization 16 quadrature amplitude modulation (DP-16QAM), etc  \cite{Lee:2016bg,PoDong:2014kj}.
However, there has been no report on integrated PBS chip that can deal with four polarizations used in BB84 QKD.
In this study, integrated PBS module using  silica-based planar lightwave circuit (PLC) chip was fabricated for the first time for BB84 protocol, and its performance was assessed it in a free-space QKD test-bed.

@@

PBS developed in this work is based on Mach-Zehnder interferometer (MZI) structure fabricated with silica PLC technology, as is shown in Fig. \ref{fig:layout}(a)\cite{Kim:2012ej, Hashizume:2015ta}.
The waveguide structure was chosen to support single mode and maximum mode matching with single mode fiber (SMF) at the operating wavelength of 780 nm, where Si-based single photon detector has high detection efficiency and atmospheric absorption is low.
Refractive indices of core and clad material were 1.4588 and 1.4537 at 780 nm, respectively, and the dimension of the waveguide core was designed as 4.3 $\mu$m $\times$ 4.3 $\mu$m.

In Fig. \ref{fig:layout}(a), the input light is split into two paths by a 3 dB splitter.
At the outputs of the splitter are connected in parallel two identical MZIs with 2$\times$2 multimode interference (MMI) coupler.
A portion of the waveguide of upper arm in each MZI was designed to have larger width of 18.5 $\mu$m.
A wide waveguide in silica PLC is known to have birefringence  due to uniaxial strain generated in the fabrication process \cite{Okuno:1994fm}.
The birefringence causes relative phase differences between H- and V-polarized lights when light reaches the  input of the MMI through the arms.
When the device is designed so that birefringence $\Delta n$ and length $L$ of the wide waveguide satisfy the condition $2\pi\Delta n/\lambda  = (2m+1) \pi$ with integer $m$, the phase difference between H- and V-polarization can be made to be 180$^\circ$.
If above condition is satisfied and the lower arm is made to provide a phase difference of 90$^\circ$ between the arms for the two polarizations, polarization separation is achieved according to the operation of MMI depicted in Fig. \ref{fig:layout}(b).

The phase relationship is determined by arm length, as described above.
But actually it changes sensitively with ambient temperature around the interferometer structure.
Therefore, micro-heaters were deposited on the arms of MZI to actively control the phase making use of the thermo-optic property of silica.

The input light may be in D/A-polarization basis as well as H/V-polarization basis, but D- and A-polarized light can not be properly separated in PLC PBS composed of rectangular waveguide.
In this study, a HWP film with its optic axis tilted by 22.5$^\circ$ was inserted at the input of the lower PBS to split D/A polarization.
Although the output of the lower MZI is annotated as D/A in Fig. \ref{fig:layout}, actual polarization of the output light is H/V.

\begin{figure}
  \centering
  \includegraphics[height=6.3cm]{./layout}
  \caption{(a) Layout of the PBS device for H/V/D/A-polarizations. 1$\times$2 splitter splits the input light into two PBSes that separate H- and V-polarization and output them to the corresponding waveguides. Lower PBS has HWP at its input so that D- or A-polarized light is converted to H- or V-polarization. (b) Schematic description of the operation of 2$\times$2 MMI. Under single port input, the two outputs show electric field with same amplitude and relative phase difference of 90$^\circ$ (upper). If there is phase difference of 90$^\circ$ between two input electric fields, one output is extinguished (lower).}
  \label{fig:layout}
\end{figure}

\subsection{Half-Wave Plate Film}

Thin film HWP was developed for converting D/A polarization to H/V polarization that can be inserted in a slit across a waveguide.
A HWP was fabricated by imposing birefringence on a polymer film \cite{Ando:1993up}.
Fixed at its two sides on a metal frame designed for elongation process, the film was stretched at an elevated temperature.
Elongation process was performed for several kinds of commercial polymer film under various conditions, and it was found that 40\% elongation of 60-$\mu$m-thick polycarbonate film at 170$^\circ$C resulted in retardance near 180$^\circ$ at the wavelength of 780 $\mu$m.
The thickness of the film after process was 53 $\mu$m.
As the film was to be used for light of D/A polarization, cutting direction was selected so that the optic axis was inclined by 22.5$^\circ$ with respect to the bottom side of the film.

\subsection{PBS Module}

Firstly, a narrow groove was formed at the input waveguides of two parallel MZIs comprising 1$\times$4 PBS with a dicing blade for the insertion of the waveplate film.
Waveplate is needed for only one MZI of the PBS, but the groove spans  both the MZIs because of the small separation of 500 $\mu$m, resulting in similar optical loss between the two MZIs.
When processed with 50-$\mu$m-thick blade, the width of the groove formed was about 62 $\mu$m.
After the waveplate film was inserted into the groove, UV-cured epoxy was injected to fix it.

Pigtailed were an SMF on the input facet and 4-channel polarization-maintaining fiber (PMF) array on the output facet.
Both the PBS chip and fibers were angle (8$^\circ$)-polished to reduce the optical return loss that influences the stable operation of LD.
The four PMFs were aligned so that the slow-axes  were oriented alternately as H-V-H-V.
Using this PMF array, the module can be used as polarization beam combiner (PBC) as well as PBS.

@@

\section{Characterization}
\subsection{PBS chip}

@@

PER was obtained by measuring the intensity from the output waveguides using a beam profiler while the current of the micro-heater was adjusted so that PER of PBS could be maximized.

The PBS chip showed different PER characteristics depending on the length of the birefringent waveguide (BRW) as shown in Fig. \ref{fig:BRW-PER}.
\begin{figure}
  \centering
  \includegraphics[width=7cm]{./BRWPER.pdf}
  \caption{Measured result of PER with birefringent waveguide length. Maximum PER of 17.1 dB was obtained when the BRW length is 2624 $\mu$m.}
  \label{fig:BRW-PER}
\end{figure}
Maximum PER was measured as 17.1 dB  when the length of BRW was 2624 $\mu$m.
From this result, the birefringence of the BRW is estimated as 1.5$\times 10^{-4}$ that is similar to that reported in Ref. \cite{Hashizume:2015ta}.

\subsection{Half-Wave Plate Film}
The optical output of the LD  was collimated and converted to D-polarized light by using a linear polarizer, and was transmitted through the waveplate film.
The resultant polarization state of the light was measured using a polarimeter (Thorlabs PAX5720IR1).
While the film exhibited spatial variation in retardance and direction of the optical axis, some areas of the film were measured to be suitable for use in PBS.
Part of the film converting D(A)-polarization to H(V)-polarization was cut out into a size of 1.5 mm $\times$ 1.0 mm for being inserted into the groove of the PBS chip.

The direction of the optic axis may have a slight offset after the cutting  or  insertion process.
Figure \ref{fig:angle_offset} shows how PER is affected by the offset angle from 22.5$^\circ$.
\begin{figure}
  \centering
  \includegraphics[width=8cm]{./offset_angle}
  \caption{PER (left axis) and its degradation (right axis) as functions of the offset angle of HWP inserted in PBS for DA-polarization. PER decreases with the offset angle, and the degradation is the larger when PER at exact angle is the higher.}
  \label{fig:angle_offset}
\end{figure}
PER gets degraded with the increase of the offset angle.
The offset angle prevents the 45$^\circ$ polarized incident light from being converted into purely V-or H-polarized light, thus reducing PER of the PBS behind the HWP.
However, Fig. \ref{fig:angle_offset} suggests that the drop of PER is not so large within  offset angle of 2$^\circ$, and  a slight angle inaccuracy does not significantly affect the overall performance.
In our study, the film cutting or treatment could be accomplished without any specialized equipment within that precision.

\subsection{PBS Module}

The polarization-splitting characteristics of the module were evaluated by receiving light from sender (Alice) of free-space QKD test-bed and measuring the optical powers from the four PMFs of the PBS module, as shown in Fig. \ref{fig:meas_setup}(a).
At the chip temperature of 21$^\circ$C and current of the micro-heater of 29 mA, the module shows PER of 22.4 dB in separating H/V polarizations, and 17.6 dB for D/A polarizations.
This is better than the result obtained from PBS chip measurement.
It is owing to both temperature optimization and better fiber-chip alignment in the module.
In chip measurement, it is difficult to align fiber with right angle to the facet of the chip.
Therefore stray light transmitted through outside of the waveguide can be coupled to unwanted output path and decrease PER of PBS.
On the other hand, the V-groove block for fiber-pigtail in module fabrication helps normal incidence of light and thus minimizes stray light.

While this polarization-splitting capability is used before single-photon detectors by receiver (Bob), the module can also be used as PBC for combining four polarization states by Alice.
Since common SMF is used as the output port in the module, there is no need to perform precise alignment so that the four polarized lights propagate along the identical path in the free space.

If four PMF-pigtailed LDs are connected to the PMFs of the PBS module, output polarizations of the LDs are converted to H-V-H-V  by the PMFs of the module, and converted to  H-V-D-A  by the HWP film in the PBS chip.
